A North Sámi to South Sámi machine translation prototype

### 2014-01-30 paper/paper.tex
add some bib references
updates
more

\usepackage[small,bf]{caption}
\usepackage{xltxtra}
\usepackage{times}

\title{North Sámi to South Sámi machine translation}
\author{Lene Antonsen \and Francis Tyers \and Trond Trosterud}
\date{}

@@

@@

@@

\section{References}

>>>>

\usepackage[small,bf]{caption}
\usepackage{xltxtra}
\usepackage{fontspec}

\defaultfontfeatures{Scale=MatchLowercase,Mapping=tex-text}

\usepackage{times}
\usepackage{natbib}

\setromanfont{Times New Roman}
\setmonofont{FreeMono}

\bibdata{paper}

\title{A North Sámi to South Sámi machine translation prototype}
\author{Lene Antonsen,\\Giellatekno,\\Tromsø\\{\tt lene.antonsen@uit.no}
\and Francis Tyers,\\Giellatekno,\\Tromsø\\{\tt ftyers@dlsi.ua.es}
\and Trond Trosterud,\\Giellatekno,\\Tromsø\\{\tt trond.trosterud@uit.no}}
\date{}

@@

% Previous work
\cite{tyers09} \cite{wiechetek10} \cite{trosterud12}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|r|}
      \hline
      Bilingual dictionary ({\tt sme}$\rightarrow${\tt sma}) & 15,204 \\ % 10776 proper names
      Transfer rules ({\tt sme}$\rightarrow${\tt sma}) & 57 \\
      \hline
    \end{tabular}
    \label{table:transfer}
    \caption{Number of bilingual dictionary entries and transfer rules}
  \end{center}
\end{table}

\begin{table}
  \begin{center}
    \begin{tabular}{|l|r|}
      \hline
      \textbf{Corpus} & \textbf{Coverage}  \\
      \hline
      Schoolbooks     & 0.0 $\pm$ 0.0 \\
      General         & 0.0 $\pm$ 0.0 \\
      \hline
    \end{tabular}
    \label{table:coverage}
    \caption{Vocabulary coverage of the system}
  \end{center}
\end{table}

@@

\bibliographystyle{apalike}
\bibliography{paper}
